---
title: "fake news study"
output: html_document
---

## intro and data exploreation

the data is from kaggle. ([view here](https://www.kaggle.com/clmentbisaillon/fake-and-real-news-dataset) )
  
it contains two csv files, *Fake.csv* and *True.csv*.  
first i explored the data: 

```{r setup, include=FALSE}
library(tidyverse)
fake = readr::read_csv(file="C:/tmp/Fake.csv")
true = readr::read_csv(file="C:/tmp/True.csv")

```


```{r exploration, include=TRUE}

glimpse(true) # glimpse true news
glimpse(fake) # glimpse fake news

```

### issue: subject mismatch

i decided to examine if subject is related to fake or true.  
however, i discoverd that the subjects are not the same between the two data sets.  
we are going to have to combine the data sets somehow.

```{r subjects, include=TRUE}
true %>% count(subject)
fake %>% count(subject)

```


## compering between subjects

```{r helper_func, include=FALSE}

minmize_subjects <- Vectorize(function(sub) {
  if (sub %in% c("politics", "politicsNews"))
  {
    return("politics")
  }
  else{
    return("non-politics")
  }
}
)
```


so we are going to   
1. **combine the data sets**  
2. **then clean up the subjects**  
we will divie the subjects up into two main ones: politics and non-politics.

```{r compare_subject, include=TRUE}
fake = fake %>% mutate(true = 0)
true = true %>% mutate(true = 1)

data = bind_rows(true, fake) %>% mutate(subject = minmize_subjects(subject))
data %>% count(subject, true)

```


thank you, bye.
